{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-28 paper/paper.tex
rephrased whole motivation section

\section{Motivation}
\label{sec:motivation}
Barthe, Rezk, Russo and Sabelfeld introduced with
their paper \cite{Barthe07} a framework to guarantee
noninterference in multithreaded programs at byte-code
level. Noninterference is a security property which
says that a program does not leak sensitive information
to an adversary. Since more and more (mobile) devices handle
an increasing number of tasks, multithreading is widely used
to prevent lock ups (when e.g. establishing a
network-connection). But often programs that are secure when they
are executed sequentially, leak information when they are
composed in parallel. This leads to an attractive channel of
information leakage.

The idea of Barthe et. al. was to close this channel by compiling
type information into the byte-code, which cause the scheduler to
treat the secure parts in a different way. The fact that many mobile
platforms already use some byte-code (e.g. Android uses a modification
of the JVM byte-code) may have been a reason for the decision to use
type-annotated byte-code.

>>>>

\section{Motivation}
\label{sec:motivation}
Protecting the confidentiality of information that is processed by
a modern computer is challenging and important, since more and more sensitive
information is fed to them. Access control and encryption are not enough to
ensure this confidentiality, because the usage of the information after the
access or decryption is not restricted. It is necessary to control the
\textit{information flow} to protect the sensitive information.
On modern mobile devices sensitive information is processed and programs
are executed multithreaded (e.g. to prevent lock ups when establishing
a network connection). Through the timing difference of the scheduled threads it
is likely that sensitive information is leaked and an attack may obtain all
sensitive data.

The idea Barthe, Rezk, Russo and Sabelfeld phrased in \cite{Barthe07} was to close
this leak (more formally called \textit{covert channel}) by annotating the byte-code
of the program (most mobile devices use some sort of byte-code e.g. Android) with security
labels according to the processed information, which causes the scheduler to hide
threads that leak information from the attacker.
